An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
start of conclusion

\subsection{Natural language processing}
\label{sec:postproc}

@@

\subsubsection{Vocabularium}

@@

\subsubsection{Language model}

@@

\section{Conclusion}
There are a lot of steps in this paper from which we can draw conclusions.
The segregation of a text image in word images is  
Word extraction is a problem

@@

The neural network

\section{Future research}
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks.
This approach does not suffer from character segmentation artifacts
This concept is explained and applied by \citep{presham}.
\section{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}

>>>>

\section{Natural language processing}
\label{sec:postproc}

@@

\subsection{Vocabularium}

@@

\subsection{Language model}

@@

\section{Future work}
Our recognition system cannot be used for real-world applications.Every individual technique has a certain error, which increases the difficulty of the next step, e.g. if word segmentation contains mistakes, character recognition becomes much harder. 
This results in a system which cannot correctly recognize handwritten text. 
However many improvements are still possible.

Firstly, given a dataset with a higher amount of training samples, the deep neural network will be able to better recognize new characters. The same applies for the neural network of oversegmentation correction.

Next %TODO Ruben

Finally, other approaches can also be considered. 
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks.
This concept is explained and applied by \citep{presham}.
%%% Dit is jouw oude tekst %%% 
There are a lot of steps in this paper from which we can draw conclusions.
The segregation of a text image in word images is  
Word extraction is a problem

@@

The neural network 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}
